### 2023-10-20 README.Rmd
added citation - 231020

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a MaxDiff, CBC, or ACBC is valid
and can also predict outside tasks that were not included in estimating
your utility scores. Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own.

@@

Chrzan, K., & Orme, B. K. (2019). <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.

@@

@@

Miaoulis, G., Parsons, H., & Free, V. (1990). Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.

>>>>

The goal of `validateHOT` is to validate the results of your validation
task (also known as holdout task) as well as a tool for simulating markets with
the results of your MaxDiff, CBC, and ACBC. 
This package is especially relevant for the [Sawtooth Software](https://sawtoothsoftware.com/) community who would like to report their analysis in *R* for open science purposes. Of course,
this package is also useful for practitioners, who would like to run the analyses
in an open source software.
The ultimate goal of these preference measurement techniques is to predict 
future behavior (Green & Srinivasan, 1990). 
A validation task is essential to ensure that your collected data of a MaxDiff, 
CBC, or ACBC is valid and can also predict outside tasks that were not included in estimating
your utility scores. The main goal  Although commercial studies often do not include a
validation/holdout task (Yang et al., 2018), it is highly recommended to do so
(Orme, 2015; Rao, 2014). This validation/holdout task does not only
help to check whether everything went right during data collection but
also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) CBC a fixed validation/
holdout task is automatically implemented. If you conduct a MaxDiff or
ACBC study, you have to program these on your own.

@@

Chrzan, K., & Orme, B. K. 2019. <em>Applied MaxDiff: A Practitioner’s Guide to Best-Worst Scaling</em> Provo, UT: Sawtooth Software.

@@

Green, Paul E.,  and Srinivasan, V. 1990. "Conjoint Analysis in Marketing: New Developments with Implications for Research and Practice." <em>Journal of Marketing 54</em>(4): 3-19.[https://doi.org/10.1177/002224299005400402](https://doi.org/10.1177/002224299005400402).

@@

Miaoulis, G., Parsons, H., & Free, V. 1990. Turf: A New Planning Approach for Product Line Extensions. <em>Marketing Research 2</em> (1): 28-40.
